### 2017-10-06 TF-vldb2018/full/sec-appendix.tex

\vspace{-1.3ex}
\stitle{Proof of Lemma~\ref{lemma-innerball}:} We will prove the lemma by contradiction. 
We know that $G_1$ is a subgraph of $G_2$, and suppose $M_1 \not\subset M_2$.
That is, there exists a pair of nodes $(u, v) \in M_1$, where $u$ is a pattern node 
and $v$ is the matched data node of $u$, but $(u, v) \not\in M_2$.
By the definition of graph simulation, from $(u, v) \in M_1$, we know that for any child node $u'$ of $u$ in $P$,
there exists a child node $v'$ of $v$ in $G_1$ such that $(u', v') \in M_1$.
From $(u, v) \not\in M_2$, we know that there exists a child node $u''$ of $u$ in $P$, 
but there exist no child nodes $v''$ of $v$ in $G_2$, such that $(u'', v'') \eps M_2$.
The process to compute maximum match relations for graph simulation is a recursive process to 
remove invalid matches from the initialized match relations $M$.
Because there exist no $u''$ in $G_2$ such that $(u'', v'') \eps M_2$, $(u, v)$ is removed from $M_2$.
Since $G_1$ is a subgraph of $G_2$, $(u, v)$ should also be removed from $M_1$, 
such that $(u, v) \not\in M_1$.
This contradicts the assumption that $(u, v) \in M_1$, and we get the lemma proved.
\eop

@@

We will prove the theorem by induction.
Given pattern $P(V_P,E_P)$ and its fragmentation \{${P}_{f1}$, \ldots, ${P}_{fh}$, $C$\},
we use $P^{C}(V_{P^{C}},E_{P^{C}})$ to denote the pattern with $V_{P^{C}}$=$V_P$ and $E_{P^{C}}$=$E_P/C$.
%we use $P^{C}(V_P,E_P/C)$ to denote the pattern with the same node set $V_P$ with $P$, and edges excluding the cut $C$ from $E_P$.
Graph simulation is an iterative process to remove unmatched nodes from the candidate nodes,
as illustrated in Fig.~\ref{alg-rsim} (lines~1-6).
We utilize $M_{C}^{k}$ (resp. $M_{i}^{k}$, $M^{k}$) to denote the match relation for $P^{C}$ (resp. $P_{fi}$, $P$) in $\ball{}$ in the $kth$ iteration.
By the definition of graph simulation, we have $M_{C}^{k}$ = $\bigcup_{i=1}^{h}M_{i}^{k}$.
To prove $M\subseteq\bigcup_{i=1}^{h}M_{i}$,
we next prove $M^{k}\subseteq M_{C}^{k}$ for each iteration instead.

\vspace{-1.8ex}
\sstab{(1)} For $k=0$, \ie the initialization step of graph simulation algorithm,
the algorithm computes the set of candidate matches for each pattern node with the same label.
As $P$ and $P^{C}$ have exactly the same node set, we have $M^{0}= M_{C}^{0}$.

\vspace{-1.8ex}
\sstab{(2)} For $k=n$ $(n\geq 0)$, if $M^{n}\subseteq M_{C}^{n}$ exists, we prove $M^{n+1}\subseteq M_{C}^{n+1}$ exists in the $(n+1)th$ iteration.
Suppose both $(u,w)\in M^{n}$ and $(u,w)\in M_{C}^{n}$ exist,
and in the $(n+1)th$ iteration, $(u,w)$ is removed from $M_{C}^{n}$ if there is a adjacent node $u'$ of $u$ in $P_{C}$,
but there exists no adjacent node $w'$ of $w$ in $G$ such that $(u',w')\in M_{C}^{n}$.
Therefore, $(u,w)$ must be removed from $M^{n}$ as $E_{P^{C}} \subseteq E_{P}$,
that is, the edge $(u,u')$ in $E_{P^{C}}$ must belong to $E_{P}$.
Thus, we have $M^{n+1}\subseteq M_{C}^{n+1}$.

@@

The proposition is correct as when $\Delta P$ comes, the perfect graphs must reside in the balls that match with each pattern fragment of $P\oplus \Delta P$.
\identifyaffball identifies \affballsx who already match with each fragment of $P$;
Or else, if there exists a fragment $P_{fi}$ of $P$ that an \affballx cannot match,
there must exist an update in $\Delta P$ on $P_{fi}$,
such that the ball may match with the updated fragment $P_{fi}\oplus \Delta P$.
Therefore, \identifyaffball filters out the balls that do not match with a fragment of $P$, and there are no pattern updates on the fragment.

@@

The proof is similar to the one of Proposition~\ref{prop-canaffballs}.
\identifyaffball filters out the balls that cannot match all $h$ pattern fragments,	and there are no data updates on the ball.

@@

The correctness of \incp \wrt $\Delta P$ is assured by
the correctness of (a) \identifyaffball (by Proposition~\ref{prop-canaffballs});
(b) \incmatch, which is assured by the correctness of \rgraphsim that has been proved in Section~\ref{sec-tsimAlg}, and the correctness of of \patedgeinsert. Indeed, \patedgeinsert only removes
nodes that are no longer valid matches in each $M(P_{fi}, \ball{[v,r]})$;
(c) \comb, whose analysis follows the same way as that for \patedgeinsert; and
(d) the early return property (by Lemma~\ref{lemma-approximation-bound}).

>>>>

\vspace{-1.3ex}
\stitle{Proof of Lemma~\ref{lemma-innerball}:} We will prove the lemma by contradiction. 
We know that $G_1$ is a subgraph of $G_2$, and suppose $M_1 \not\subset M_2$.
That is, there exists a pair of nodes $(u, v) \in M_1$, where $u$ is a pattern node 
and $v$ is the matched data node of $u$, but $(u, v) \not\in M_2$.
By the definition of graph simulation, from $(u, v) \in M_1$, we know that for any child node $u'$ of $u$ in $P$,
there exists a child node $v'$ of $v$ in $G_1$ such that $(u', v') \in M_1$.
From $(u, v) \not\in M_2$, we know that there exists a child node $u''$ of $u$ in $P$, 
but there exist no child nodes $v''$ of $v$ in $G_2$, such that $(u'', v'') \eps M_2$.
The process to compute maximum match relations for graph simulation is a recursive process to 
remove unmatched nodes from the initialized match relations $M$.
Because there exist no $u''$ in $G_2$ such that $(u'', v'') \eps M_2$, $(u, v)$ is removed from $M_2$.
Since $G_1$ is a subgraph of $G_2$, $(u, v)$ should also be removed from $M_1$, 
such that $(u, v) \not\in M_1$.
This contradicts the assumption that $(u, v) \in M_1$, and we get the lemma proved.
\eop

@@

We will prove the theorem by induction.
Given pattern $P(V_P,E_P)$ and its fragmentation \{${P}_{f1}$, \ldots, ${P}_{fh}$, $C$\},
we use $P^{C}(V_{P^{C}},E_{P^{C}})$ to denote the pattern with $V_{P^{C}}$=$V_P$ and $E_{P^{C}}$=$E_P/C$.
%we use $P^{C}(V_P,E_P/C)$ to denote the pattern with the same node set $V_P$ with $P$, and edges excluding the cut $C$ from $E_P$.
Graph simulation is an iterative process to remove unmatched nodes from the candidate nodes,
as illustrated in procedure \rgraphsim in Fig.~\ref{alg-rsim}.
We utilize $M_{C}^{k}$ (resp. $M_{i}^{k}$, $M^{k}$) to denote the match relation for $P^{C}$ (resp. $P_{fi}$, $P$) in $\ball{}$ in the $kth$ iteration.
By the definition of graph simulation, we have $M_{C}^{k}$ = $\bigcup_{i=1}^{h}M_{i}^{k}$.
To prove $M\subseteq\bigcup_{i=1}^{h}M_{i}$,
we next prove $M^{k}\subseteq M_{C}^{k}$ for each iteration instead.

\vspace{-1.8ex}
\sstab{(1)} For $k=0$, \ie the initialization step of graph simulation algorithm,
the algorithm computes the set of candidate matches for each pattern node.
As $P$ and $P^{C}$ have exactly the same node set, we have $M^{0}= M_{C}^{0}$.

\vspace{-1.8ex}
\sstab{(2)} For $k=n$ $(n\geq 0)$, if $M^{n}\subseteq M_{C}^{n}$ holds, we prove $M^{n+1}\subseteq M_{C}^{n+1}$ holds in the $(n+1)th$ iteration.
Suppose both $(u,w)\in M^{n}$ and $(u,w)\in M_{C}^{n}$ hold,
and in the $(n+1)th$ iteration, $(u,w)$ is removed from $M_{C}^{n}$ if there is an adjacent node $u'$ of $u$ in $P_{C}$,
but there exists no adjacent node $w'$ of $w$ in $G$ such that $(u',w')\in M_{C}^{n}$.
Therefore, $(u,w)$ must be removed from $M^{n}$ as $E_{P^{C}} \subseteq E_{P}$,
that is, the edge $(u,u')$ in $E_{P^{C}}$ must belong to $E_{P}$.
Thus, we have $M^{n+1}\subseteq M_{C}^{n+1}$.

@@

The proposition is correct as when $\Delta P$ comes, the perfect subgraphs must reside in the balls that match all pattern fragments of $P\oplus \Delta P$.
\identifyaffball identifies \affballsx who already match all fragments of $P$;
Or else, if there exists a fragment $P_{fi}$ of $P$ that an \affballx cannot match,
there must exist an edge/node deletion in $\Delta P$ on $P_{fi}$,
such that the ball may match the updated fragment $P_{fi}\oplus \Delta P$.
Thus, \identifyaffball filters out the balls that cannot not match at least one fragment of $P$, and there are no deletion updates on the fragment.

@@

The proof is similar to the one of Proposition~\ref{prop-canaffballs}.
\identifyaffball filters out the balls that cannot match all pattern fragments,	and there are no data updates on the ball.

@@

The correctness of \incp \wrt $\Delta P$ is assured by
the correctness of (a) \identifyaffball (by Proposition~\ref{prop-canaffballs});
(b) \incmatch, which is assured by the correctness of \rgraphsim that has been proved in Section~\ref{sec-tsimAlg}, and the correctness of of \patedgeinsert. Indeed, \patedgeinsert only removes
nodes that are no longer valid matches in each $M(P_{fi}, \ball{[v,r]})$;
(c) \comb, whose analysis follows the same way as that of \patedgeinsert; and
(d) the early return property (by Lemma~\ref{lemma-approximation-bound}).
